---
title: "Practical Machine Learning WriteUp"
author: "Predrag Mihailovic"
date: "May 10, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Asignment
In this project, I have to develop a machine learning algorythm to predict how well 6 participants do the activities.

The training data is https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

Testing should be performed on https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

Data source is  http://groupware.les.inf.puc-rio.br/har


### Reading the files, and cleaning the data
```{r}
rawData=read.csv('pml-training.csv',na.strings=c('','NA'))
cleanedData=rawData[,!apply(rawData,2,function(x) any(is.na(x)) )]
mData=cleanedData[,-c(1:7)]
```


### Training

Necessary packages

```{r }
library('randomForest')
library('caret')
library('e1071')
```


Testing data will be divided in two groups. The first will be 0.6
```{r }
partititions=createDataPartition(y=mData$classe, p=0.6, list=FALSE)
trainingData=mData[partititions,]
testingData=mData[-partititions, ]
dim(trainingData);dim(testingData)
```

So there are 11776 record in the first group and 7846 in the second

Using Random Forest paradigm I predict outcome

```{r }
model=randomForest(classe~., data=trainingData, method='class')
pred=predict(model,testingData, type='class')
matrixData=confusionMatrix(pred,testingData$classe)
save(matrixData,file='matrixData.RData')
```

```{r }
setwd('E:/Personal/Coursera/projects')
load('matrixData.RData')
matrixData$table
```

Check the accuracy
```{r }
matrixData$overall[1]
```

So the accuracy is 99.31%, and the error rate will be .69%

### Prediction

Reading testing data set
```{r }
rawDataTest=read.csv('pml-testing.csv',na.strings=c('','NA'))
cleanedDataTest=rawDataTest[,!apply(rawDataTest,2,function(x) any(is.na(x)) )]
mDataTest=cleanedDataTest[,-c(1:7)]
```

Analyse
```{r }
predictedData=predict(model,mDataTest,type='class')
save(predictedData,file='predictedData.RData')
```

And finally
```{r }
setwd('E:/Personal/Coursera/projects')
load('predictedData.RData')
print(predictedData)
```
